# Creatinine Time Series

```{r 05_creatinine_ts, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "05_creatinine_ts.R"))
```

```{r combine_blood_gas_bio_chem, echo=FALSE}
```

## Example Creatinine Plot

Below you can see an example time series plot of creatinine for a patient admitted twice into ICU. Both the BioChem and ABG results are shown.

```{r example_creatinine_plot, echo=FALSE, fig.height=4}
```

## Comparison Between BioChem and ABG

This uses a [@Udy2009] to determine the difference between the two measurements as:
Cr<sub>ABG</sub> - Cr<sub>BioChem</sub> = `r blood_gas_adjust`.
Below you can see that this is still not perfect as the centreline is not zero for
all cases.

```{r plot_blood_gas_vs_bio_chem, echo=FALSE, message=FALSE, warning=FALSE, fig.height=12}
```

## Compute all Creatinine Changes

```{r aki_cr_ch_fun, echo=FALSE}
```

```{r admission_ts, echo=FALSE}
```

Insert image to show the creatinine changes and nomenclature

## Exploration

Each of the possible creatinine change events is calculated and plotted below. It shows that for admissions with no AKI, the creatinine change is approximately symmetric. <!-- Add some additional words -->

```{r heatmap_plot, echo=FALSE, fig.width=8}
```
