# Creatinine Time Series

```{r echo=FALSE}
knitr::opts_chunk$set(
    echo = FALSE, message = FALSE, cache = TRUE,
    collapse = TRUE, comment = "#>", tidy = TRUE
)
```

```{r 05_cr_ts_data, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "05_cr_ts_data.R"))
```

```{r combine_blood_gas_bio_chem}
```

## Example Creatinine Plot

Below you can see an example time series plot of creatinine for a patient admitted twice into ICU. Both the BioChem and ABG results are shown.

```{r example_creatinine_plot, fig.height=4}
```

## Comparison Between BioChem and ABG

This uses a [@Udy2009] to determine the difference between the two measurements as:
Cr<sub>ABG</sub> - Cr<sub>BioChem</sub> = `r blood_gas_adjust`.
Below you can see that this is still not perfect as the centreline is not zero for
all cases.

```{r plot_blood_gas_vs_bio_chem, fig.height=12, warning=FALSE}
```

## Compute all Creatinine Changes

In total there were 8,817 ABG and Bio Chem Cr measurements which corresponds to 251,652 Cr change episodes.

Of these creatinine change episodes, 43,404 were in admissions that did not have AKI and 28,095 change episodes were before onset of AKI.
There were 180,153 Cr change episodes after the onset of AKI and these were discarded.

```{r 06_cr_changes, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "06_cr_changes.R"))
```

```{r generate_cr_ch_function}
```

```{r generate_cr_changes}
```

```{r cr_changes_overview}
```

<!--- Insert image to show the creatinine changes and nomenclature -->

## Exploration

Each of the possible creatinine change events is calculated and plotted below.

It shows that for admissions with no AKI, the creatinine change is approximately symmetric.

In admissions with AKI, the distribution of $\Delta\text{Cr}$ is positively skewed. This indicates that $\Delta\text{Cr}$ is a good predictor of AKI.

<!-- Add some additional words -->

```{r heatmap_plot, fig.width=8}
```
