# Cr ch only

```{r echo=FALSE}
knitr::opts_chunk$set(
    echo = FALSE, message = FALSE, cache = TRUE,
    collapse = TRUE, comment = "#>", tidy = TRUE
)
```

Univariable logistic regression to determine the baseline model and AUC value.

```{r 22_cr_ch_only, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "22_cr_ch_only.R"))
```

## Cr change as Continuous Variable

Here $\Delta\text{Cr}\,(\mu\text{mol/L})$ denotes the change in creatinine during the defined length of
the small change in creatinine change episode.

$$
\begin{align}
\log(\text{Odds}(\text{AKI}=1)) &= \beta_0 + \beta_1\cdot\Delta\text{Cr}
\end{align}
$$

### Previous Study

Below is an example of creatinine changes in episodes 3-4 hrs in duration occurring 8-16 hrs before AKI.

```{r prev_study_cont}
```

### Best AUC for AKI in 8-16hrs

Now, run various other episode durations to determine if there is an "optimal" duration.

```{r range_cr_ch_cont_only}
```

## Cr change Gradient as Binary Variable

Here $\left[\frac{\Delta\text{Cr}}{\Delta\text{t}}\right]_\text{B}$ denotes a binary variable where
the gradient of the creatinine change is greater than $1\,(\mu\text{mol/L/hr})$ or not.

$$
\begin{align}
\log(\text{Odds}(\text{AKI}=1)) &= \beta_0 + \beta_1\cdot\left[\frac{\Delta\text{Cr}}{\Delta\text{t}}\right]_\text{B}
\end{align}
$$

### Previous Study

Below is an example of creatinine changes in episodes 3-4 hrs in duration occurring 8-16 hrs before AKI.

```{r prev_study_bin}
```

### Best Manually Chosen Model

Now, run various other episode durations to determine if there is an "optimal" duration.

```{r range_cr_ch_bin_only}
```

Here you can see that while $\left[\frac{\Delta\text{Cr}}{\Delta\text{t}}\right]_\text{B}$
is clinically more intuitive to understand, it has a smaller predicitive power compared to
$\Delta\text{Cr}\,(\mu\text{mol/L})$

For both explanatory variables, there is a distinct peak in AUC for episode durations
[6-7] and [7-8] hrs long.
