# Known Risk Factors

Multivariable logistic regression to determine the baseline model and AUC value.

```{r 21_base_no_cr_ch, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "21_base_no_cr_ch.R"))
```

## Baseline without Comorbidities

$$
\begin{align}
\log(\text{Odds}(\text{AKI}=1)) &= \beta_0 + \beta_1\cdot\text{Age} + \beta_2\cdot\text{APACHE}_\text{II} \\
  &\qquad + \beta_3\cdot\text{APACHE}_\text{III} + \beta_4\cdot\text{Cr}_\text{Baseline}
\end{align}
$$

```{r base_no_comorbidities}
```

## Baseline with Comorbidities


$$
\begin{align}
\log(\text{Odds}(\text{AKI}=1)) &= \beta_0 + \beta_1\cdot\text{Age} + \beta_2\cdot\text{APACHE}_\text{II} + \beta_3\cdot\text{APACHE}_\text{III} \\
  &\qquad + \beta_4\cdot\text{Cr}_\text{Baseline} + \beta_5\cdot\text{PCs_Cardio} + \beta_6\cdot\text{Vasopressor} \\
  &\qquad + \beta_7\cdot\text{Diabetes} + \beta_8\cdot\text{AF} + \beta_9\cdot\text{IHD} + \beta_{10}\cdot\text{HF} \\
  &\qquad + \beta_{11}\cdot\text{HT} + \beta_{12}\cdot\text{PVD} + \beta_{13}\cdot\text{ChronicLiverDisease}
\end{align}
$$

```{r base_with_comorbidities}
```

From the output, you can see that some variables are more significant than others.

## Baseline with only Significant Factors

Consider only the more significant variables.

$$
\begin{align}
\log(\text{Odds}(\text{AKI}=1)) &= \beta_0 + \beta_1\cdot\text{PCs_Cardio} + \beta_2\cdot\text{Vasopressor} \\
  &\qquad + \beta_3\cdot\text{HT} + \beta_{4}\cdot\text{ChronicLiverDisease}
\end{align}
$$

```{r base_significant_only}
```

You can see that there is no significant improvement. The decision was made to retain all the variables in the subsequent analyses as they may become significant once the creatinine change events are accounted for.
