---
title: "The predictive value of small short-term creatinine increases for the development of acute kidney injury detected by arterial blood gases in a clinical context for critically ill patients"
author: "Lisa Toh, Alwin Wang"
date: "`r Sys.Date()`"
output:
  html_document:
    number_sections: true
bibliography:
  - "../bib/references.bib"
  - "../bib/R-references.bib"
biblio-style: apalike
link-citations: yes
editor_options:
  markdown:
    wrap: 72
---

```{r setup, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  message = FALSE,
  cache = TRUE,
  collapse = TRUE,
  comment = "#>",
  tidy = TRUE
)

knitr::opts_template$set(silent = list(
  warning = FALSE,
  results = 'hide')
)


rel_path = "../.."
read_R <- function(file) readLines(file.path(rel_path, "R", file))
```

```{r 00_config, include=FALSE, cache=FALSE}
# Cannot source this directly or it will override rel_path
knitr::read_chunk(file.path(rel_path, "R/00_config.R"))
```

```{r, load_library_function, opts.label='silent'}
```

```{r environment_setup, opts.label='silent'}
```

# Abstract {.unnumbered}

## Aim {.unnumbered}

New Arterial Blood Gas (ABG) technology provides accurate and validated
point-of-care creatinine measurement. Such technology makes it possible
to detect small, short-term increases in creatinine levels. These
changes alone however lack clinical context. We aimed to improve the
predictive value of small, short-term creatinine increases for the
development of Acute Kidney Injury (AKI) in critically ill patients by
incorporating clinically available information.

## Methods {.unnumbered}

In this prospective cohort study, we identified all creatinine
measurements from point-of-care arterial blood gases and laboratory
biochemistry results during a patient's intensive care unit admission
until the development of acute kidney injury, or discharge, or death,
whichever occurred first. We evaluated the predictive value of the
small, short-term creatinine changes between creatinine measurements for
the development of acute kidney injury, as defined by the Kidney
Disease: Improving Global Outcomes criteria. We evaluated the predictive
value of these creatinine increases over varying time periods for AKI
development in multivariable analysis with known risk factors,
co-morbidities and other clinically available data.

## Results {.unnumbered}

**TO BE FIXED UP**

We screened a convenience sample of 830 patients and excluded 443
(53.4%) patients [AKI on admission (208; 47%), weekend admission (91;
21%) and other pre-defined exclusion criteria (144; 32%)]. The 387
(46.6%) eligible patients had 3,974 creatinine measurements on ABGs and
biochemistry results, which generated 71,499 creatinine change episodes,
excluding creatinine measurements after AKI development. In
multivariable modelling, creatinine increases of ≥1 µmol/L/h over 6 to 7
hours had an odds ratio of 3.14 (95% CI 1.82 -- 5.43) for the
development of AKI in 8 to 16 hours after the creatinine increase. The
multivariable model with these creatinine increases had an 81.5%
sensitivity, 74.2% specificity and 0.85 area under the curve for AKI
development in 8 to 16 hours.

## Conclusion {.unnumbered}

In combination with known risk factors, frequent creatinine assessment
to detect small, short-term creatinine increases provides a novel and
rapid method of predicting AKI in critically ill patients.

# Introduction

[1/2 Page Approx]

-   Acute kidney injury (AKI) is common in critically-ill patients
    admitted to the intensive care unit (ICU), and is associated with
    high morbidity and mortality in the critically ill population. Its
    pathogenesis is still poorly understood, with limited ability to
    predict its occurrence. Failure to improve outcomes of patients with
    AKI may be linked to delays in its detection.

-   Creatinine changes alone lack context. In order to improve
    predictability of Cr from ABG likely obtaining readily clinically
    available info will improve the ability of serum cr to predict
    subsequent AKI.

-   Assessment of small short term cr changes have limited predictive
    value

```{r copy_cr_ch_heatmap, opts.label='silent'}
dir.create("images/", showWarnings = FALSE)
file.copy("../images/heatmap_AKI_ICU.png", "images/")
```

![Distribution of Cr ch epis for patients with and without
AKI](images/heatmap_AKI_ICU.png)

-   Aim to develop a model that uses short term changes in serum cr and
    clinical info to improve predictive values

-   High performing model can be developed when taking clinical
    characteristics as well as short term cr changes for acute kidney
    injury

# Methods

[1/2 Page Approx]

## Design and Setting

This single-centre prospective observational cohort study had ethics
approval from the Austin Health (LNR/17/Austin/618) and Monash
University Human Research Ethics Committees (reference number: 12216)
with consent waived due to the observational nature of the study.

## Study Cohort

This study was conducted in a tertiary referral university hospital ICU.
All patients admitted to the ICU between 5 February and 16 July 2018
were considered for enrolment. We excluded patients who were \<18 years
old, had AKI as defined by the Kidney Disease: Improving Global Outcomes
(KDIGO) definition on ICU admission, had end-stage kidney disease or a
kidney transplant, were a weekend admission, were receiving end-of-life
care or had no urinary catheter or arterial line in situ.

\*TODO: Reference KDIGO\*

## Creatinine Measurements

We identified all creatinine measurements from point-of-care arterial
blood gases and laboratory biochemistry results during a patient's ICU
admission until the development of AKI, or ICU discharge, or death,
whichever occurred first. Creatinine measurements on point-of-care ABGs
and laboratory biochemistry samples were only performed for clinical
purposes as directed by the treating team, independent from the data
collectors.

Point-of-care creatinine measurements on ABGs were conducted on the
Radiometer ABL800 Flex® analyser (Radiometer Medical ApS, Brønshøj,
Denmark). This uses a non-isotope dilution mass spectrometry (non-IDMS)
enzymatic assay and a two-electrode amperometric technique \*insert
reference\*. At one electrode, creatinine and creatine are converted to
hydrogen peroxide with enzyme catalysis, then hydrogen peroxide is
oxidised to hydrogen ions, oxygen and electrons. \*insert reference\*.
The second electrode repeats the process with creatine only and the
difference in the electrical current between the two gives the
creatinine concentration. \*insert reference\*

Creatinine measurements on laboratory biochemistry samples are analysed
using the Jaffé method on a biochemical analyser (Hitachi 747; Roche
Diagnostics, Sydney, Australia).

## Creatinine Change Episodes

\*where to put correctino for biochem UEC creatinine vs ABG creatinine\*

We calculated the small change in creatinine between any two creatinine
measurements for each patient prior to AKI development, discharge from
ICU or death, whichever occurred first. Patients were monitored for AKI
development as defined by the KDIGO creatinine and urine output
criteria. A patient's baseline creatinine was defined as the lowest
creatinine measurement in the 3 months prior to ICU admission.

## Outcomes

The primary outcome was the development of stages 2 and 3 AKI in a
clinically useful time period after a creatinine change episode. The
target time window from the end of the creatinine change episode to AKI
development was varied in order to evaluate the utility of small
creatinine changes as an independent predictor. A range of durations
over which the creatinine change episode occurred were also evaluated.

The secondary outcome was development of a high-performing model to
predict (stages 2 and 3) AKI in a clinically useful time period after a
creatinine change episode. This model incorporated patient
characteristics such as co-morbidities to augment the predictive value
of small creatinine changes. We assessed the additive predictive value
of age, baseline creatinine value, recent cardiac surgery, use of
vasopressors, APACHE II and III scores and presence of the
co-morbidities diabetes mellitus, atrial fibrillation, ischaemic heart
disease, cardiac failure, hypertension, peripheral vascular disease and
chronic liver disease.

-   In total there were 8,817 ABG and Bio Chem Cr measurements which
    corresponds to 251,652 Cr change episodes. Of these creatinine
    change episodes, 43,404 were in admissions that did not have AKI and
    28,095 change episodes were before onset of AKI. There were 180,153
    Cr change episodes after the onset of AKI and these were discarded.

```{r copy_flow_chart, opts.label='silent'}
dir.create("images/", showWarnings = FALSE)
file.copy("../images/screening-flow-chart.svg", "images/")
```

![Screening flow chart](images/screening-flow-chart.svg)

## Statistical Analysis

Statistical analyses were performed in "R" (R Foundation for Statistical
Computing, Vienna, Austria, version 4.0.3) using RStudio (RStudio Inc.,
Boston, Massachusetts, version 1.4.1056). Categorical data were
expressed as percentages and compared using chi square tests or Fisher's
exact test if greater than 20% of the contingency table had frequencies
less than 5. Non-parametric data were summarised with median and
interquartile range and compared using Mann-Whitney U tests. An alpha of
less than 0.05 was used to reject the null hypothesis.

The predictive value of small short-term point-of-care creatinine change
episodes and continuous creatinine increases for AKI were assessed using
univariate and multivariable logistic regressions and area under the
receiver operating characteristic (AUROC). AUROC quality was defined as:
excellent (0.9-1.0), very good (0.8-0.9), good (0.7-0.8), fair (0.6-0.7)
and poor (0.5-0.6). Optimal cut-offs on the receiver operating
characteristics were determined using the Youden Index.

Multivariable logistic regression was performed on the above listed
patient characteristic variables. From this, a performant, parsimonious
model was selected using backward stepwise selection based on Bayesian
information criteria. To determine the best time windows for the
creatinine change episode and time to development of AKI, a combination
of coarse grid search and Bayesian optimisation were employed. A
heuristic was used to balance clinical relevance of the time period
during which AKI was detected, the time period over which the creatinine
change occurred and model performance.

# Results

## Patient Demographics

We screened a convenience sample of 830 patients and studied 384
patients with a median age of XX (IQR XX to XX years). Patient
characteristics are presented in Table 1. The 384 patients had a total
of 3,960 creatinine measurements on ABGs and biochemistry results which
generated 71,499 creatinine change episodes, excluding creatinine
measurements after AKI development. Creatinine measurements ranged from
XX to XX with the median creatinine XX (IQR XX to XX µmol/L). XX (XX%)
patients studied developed AKI in ICU and XX (XX%) patients developed
stages 2 or 3 AKI in ICU. The median time from ICU admission to AKI
diagnosis was XX hours and the median time from ICU admission to stage 2
or 3 AKI was XX hours.

## Creatinine Change as an Independent Predictor of AKI

\*TODO\*

## Augmentation of the Predictive Value of Creatinine Change with Patient Demographics

The final multivariable model incorporated XXX, XXX, in addition to
creatinine change.

In multivariable modelling, creatinine increases of ≥1 µmol/L/h over XX
to XX hours had an odds ratio of XXX (95% CI XXX -- XXX) for the
development of AKI in XX to XX hours after the creatinine increase. The
multivariable model with these creatinine increases had an XXX%
sensitivity, XXX% specificity and XXX area under the curve for AKI
development in XX to XX hours.

<!-- R Analysis: Load Data -->

```{r 01_load_data, code=read_R("01_load_data.R"), opts.label='silent'}
```

```{r 02_screening_log, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "02_screening_log.R"))
```

```{r join_demo_screen_log_sheets_function}
```

```{r screen_log_all}
```

```{r screen_log_apache}
```

```{r 03_data_set, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "03_data_set.R"))
```

```{r find_cols_function}
```

```{r merge_data_sets_outcomes}
```

```{r merge_data_sets}
```

```{r 04_merge_all, code=read_R("04_merge_obs.R"), opts.label='silent'}
```

```{r 05_cr_ts_data, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "05_cr_ts_data.R"))
```

```{r combine_blood_gas_bio_chem}
```

```{r 06_cr_changes, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "06_cr_changes.R"))
```

```{r generate_cr_ch_function}
```

```{r generate_cr_changes}
```

<!-- R Analysis: Demographics -->

<!-- Should have columns for each of the models -->

<!-- R Analysis: Analysis -->

```{r 30_aki_dev, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "30_aki_dev.R"))
```

```{r analysis_ts}
```

```{r aki_dev_wrapper}
```

```{r summarise_cutpoint_function}
```

```{r 31_aki_optim, include=FALSE, cache=FALSE}
knitr::read_chunk(file.path(rel_path, "R", "31_aki_optim.R"))
```

```{r aki_optim_wrapper}
```

```{r optim_cr_ch_only}
set.seed(8)
optim_in = rbind(
  c(6.87, 1.40, 9.61, 3.06),  # AUC 0.7592 | 0.40, 152
  cbind(
    rnorm(10, 6.87, 0.5),
    rnorm(10, 1.40, 0.5),
    rnorm(10, 9.61, 0.5),
    rnorm(10, 3.06, 0.5)
  ),
  c(7.43, 1.15, 10.30, 3.50), # AUC 0.7269 | 0.36, 138
  cbind(
    rnorm(10,  7.43, 0.5),
    rnorm(10,  1.15, 0.5),
    rnorm(10, 10.30, 0.5),
    rnorm(10,  3.50, 0.5)
  ),
  c(6.97, 1.10, 9.63, 5.12), # AUC 0.7243 | 0.37, 142
  cbind(
    rnorm(10,  6.97, 0.5),
    rnorm(10,  1.10, 0.5),
    rnorm(10,  9.63, 0.5),
    rnorm(10,  5.12, 0.5)
  ),
  c(7.28, 1.26, 11.80, 3.41), # AUC 0.7065 | 0.37, 143
  cbind(
    rnorm(10,  7.28, 0.5),
    rnorm(10,  1.26, 0.5),
    rnorm(10, 11.80, 0.5),
    rnorm(10,  3.41, 0.5)
  )
)
heuristic_calc <- function(AUC, per_admin_in){return(AUC)}
optim_only_model <- aki_optim_wrapper(
  optim_in,
  outcome_var = "AKI_ICU",
  baseline_predictors = "",
  cr_predictors = "",
  add_gradient_predictor = 1,
  lower = c(3, 0.1, 8, 3),
  upper = c(10, 3, 12, 48)
)
kable(head(optim_only_model$optim_summary, 20))
```

```{r optim_cr_ch_only_model}
only_model <- aki_dev_wrapper(
  outcome_var = "AKI_ICU",
  baseline_predictors = "",
  cr_predictors = NULL,
  del_t_ch_hr_range = c(6.17, 7.57),
  del_t_aki_hr_range = c(9.61, 12.67),
  add_gradient_predictor = 1,
  all_data = TRUE,
  analysis_data = analysis_df
)
kable(only_model$params)
kable(publish(only_model$model, print = FALSE, digits = c(2, 3))$regressionTable,
      align = c('l', 'c', 'c', 'c', 'c'))
kable(summarise_cutpoint(only_model), align = c('l', 'r'))
```

```{r known_risk_factors}
baseline_df <- analysis_df %>%
  select(-DateTime_Pathology_Result:-del_t_aki_hr) %>%
  unique(.)

base_model <- aki_dev_wrapper(
  outcome_var = "AKI_ICU",
  baseline_predictors = c(
    "Age + APACHE_II + APACHE_III + Baseline_Cr",
    "PCs_cardio + Vasopressor + Diabetes + AF + IHD + HF + HT + PVD + Chronic_liver_disease"
  ),
  all_data = TRUE,
  analysis_data = baseline_df
)
kable(base_model$params)
kable(publish(base_model$model, print = FALSE, digits = c(2, 3))$regressionTable,
      align = c('l', 'c', 'c', 'c', 'c'))
kable(summarise_cutpoint(base_model), align = c('l', 'r'))
```

```{r known_risk_factors_reduced, include = FALSE}
base_model_r <- aki_dev_wrapper(
  outcome_var = "AKI_ICU",
  baseline_predictors = c(
    "Age + APACHE_II + APACHE_III + Baseline_Cr",
    "PCs_cardio + Vasopressor + Diabetes + AF + IHD + HF + HT + PVD + Chronic_liver_disease"
  ),
  stepwise = TRUE,
  k = "AIC",
  all_data = TRUE,
  analysis_data = baseline_df
)
kable(base_model_r$params)
kable(publish(base_model_r$model, print = FALSE, digits = c(2, 3))$regressionTable,
      align = c('l', 'c', 'c', 'c', 'c'))
kable(summarise_cutpoint(base_model_r), align = c('l', 'r'))
```

```{r optim_multi}
set.seed(8)
# Consider showing data as clusters e.g. p1, p2, p3, p4?
optim_in = rbind(
  c(9.90, 2.14, 11.79, 3.03), # AUC 0.8994 | 0.39, 150 Clinically not relevant
  c(6.84, 1.15,  8.08, 3.55), # AUC 0.8856 | 0.40, 153
  c(7.20, 1.34,  8.03, 4.48), # AUC 0.8664 | 0.42, 161
  c(7.27, 1.07, 11.70, 3.88), # AUC 0.8977 | 0.37, 143 Exceptional!
  # cbind(
  #   rnorm(10,  7.27, 0.5),
  #   rnorm(10,  1.07, 0.5),
  #   rnorm(10, 11.70, 0.5),
  #   rnorm(10,  3.88, 0.5)
  # ),
  c(6.55, 0.95,  8.48, 12.31), # AUC 0.8489 | 0.41, 157 Clinically good
  c(6.51, 1.04, 11.82, 21.64), # AUC 0.8220 | 0.42, 160 Clinically great
  c(6.47, 0.56,  9.69, 29.02), # AUC 0.8642 | 0.35, 135 Clinically excellent
  c(7.77, 0.82, 11.57, 44.67), # AUC 0.8149 | 0.42, 162 Clinically excellent
  c(7.87, 1.00, 10.58, 46.16), # AUC 0.8172 | 0.47, 179 Clinically excellent
  c(6.41, 0.71,  9.17, 38.66), # AUC 0.8198 | 0.40, 153 Clinically excellent
  c(6.51, 0.97, 11.00, 34.25)  # AUC 0.7955 | 0.42, 160 Clinically excellent
)
heuristic_calc <- function(AUC, per_admin_in){
  return((1/2 + 1/2*tanh(11*(AUC - 0.90 + 0.1)) +
            1/2 + 1/2*tanh(11*(per_admin_in - 0.40 + 0.1)))/2)
}
optim_multi_model <- aki_optim_wrapper(
  optim_in,
  outcome_var = "AKI_ICU",
  baseline_predictors = c(
    "Age + APACHE_II + APACHE_III + Baseline_Cr",
    "PCs_cardio + Vasopressor + Diabetes + AF + IHD + HF + HT + PVD + Chronic_liver_disease"
  ),
  cr_predictors = "cr",
  add_gradient_predictor = 1,
  stepwise = FALSE,
  k = "mBIC",
  lower = c(3, 0.1, 8, 3),
  upper = c(10, 3, 12, 48),
  cluster = TRUE
)
kable(head(optim_multi_model$optim_summary, 20))
```

# Discussion

## Main Findings

## Relationship with Previous Studies

## Study Implications

## Strengths and Limitations

# Conclusion
