---
title: "01-Data-Merge"
author: "Alwin Wang"
date: "07/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE, cache=TRUE)
source("../R/001-library-manager.R")
# soruce other files too

load_library()
```

## Merge Observations from Data Collection:

### Load Data {ref:}

Changes were made to the Excel data collection worksheets in order to further clean the data prior to loading.

* Creatinine change in oliguria

  - 'AKI & outcomes'!D120: Cell changed from "4/18" to blank. `read_excel` correctly reads this column as POSIXct [4 Jan 2020]
  - 'Data set'!D1: Column name changed from "Time_olig_episode" to "Time_olig_epis". Consistent with other column names and conversion of individual date and time columns into single DTTM columns

```{r data locations}
oliguria_xlsx_path     = file.path("../data", "Creatinine change in oliguria 4.1.20.xlsx" )
creatinine_xlsx_path   = file.path("../data", "Small changes in creatinine 27.9.18.xlsx"  )
demographics_xlsx_path = file.path("../data", "Demographics pts screened out.xlsx"        )
creat_furo_xlsx_path   = file.path("../data", "ED_ICU_Creatinine_Furosemide.xlsx"         )
```

