---
title: "01-Data-Merge"
author: "Alwin Wang"
date: "07/01/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, cache=TRUE)
source("../R/001-library-manager.R")
# soruce other files too

load_library()
```

# Merge Observations from Data Collection

## Load Data

Changes were made to the Excel data collection worksheets in order to further clean the data prior to loading.

* Creatinine change in oliguria

  - `'AKI & outcomes'!D120`: Cell changed from "4/18" to blank. `read_excel` correctly reads this column as POSIXct [4 Jan 2020]
  - `'Data set'!D1`: Column name changed from "Time_olig_episode" to "Time_olig_epis". Consistent with other column names and conversion of individual date and time columns into single DTTM columns

Data locations:

```{r data locations setup, echo=FALSE}
# Use chunk option `code = readLines("../R/000-data-source.R"), echo=TRUE` but this includes comments
data_source <- readLines("../R/000-data-source.R")
data_locations = data_source[!(data_source == "" | grepl("#", data_source))]
knitr::read_chunk(data_locations)
```

```{r data locations, echo=TRUE}
# <<answer>>
```

```{r load excel files}
load_excel_files <- function() {
  oliguria_xlsx <- list(
    demographic = read_excel(oliguria_xlsx_path, "Patient Demographics"),
    data_set    = read_excel(oliguria_xlsx_path, "Data set"            ),
    outcomes    = read_excel(oliguria_xlsx_path, "AKI & outcomes"      ),
    screen_log  = read_excel(oliguria_xlsx_path, "Screening log"       )
  )
  creatinine_xlsx <- list(
    demographic = read_excel(creatinine_xlsx_path, "Patient Demographics"),
    data_set    = read_excel(creatinine_xlsx_path, "Data set"            ),
    outcomes    = read_excel(creatinine_xlsx_path, "AKI & outcomes"      ),
    screen_log  = read_excel(creatinine_xlsx_path, "Screening log"       )
  )
  demographics_xlsx <- list(
    num_creatinine = read_excel(demographics_xlsx_path, "no cr change"       ),
    num_oliguria   = read_excel(demographics_xlsx_path, "no oliguria"        ),
    neither_cr_ol  = read_excel(demographics_xlsx_path, "neither cr nor olig")
  )
  creat_furo_xlsx <- list(
    blood_gas    = read_excel(creat_furo_xlsx_path, "Blood Gas"              ),
    bio_chem     = read_excel(creat_furo_xlsx_path, "BioChem"                ),
    lowest_creat = read_excel(creat_furo_xlsx_path, "Lowest Creatinine Level"),
    furosemide   = read_excel(creat_furo_xlsx_path, "Medication"             )
  )
  
  names(creatinine_xlsx$screen_log)[ncol(creatinine_xlsx$screen_log)] <- "Comment"
  names(oliguria_xlsx  $screen_log)[ncol(oliguria_xlsx  $screen_log)] <- "Comment"
  
  xlsx_data <- list(
    oliguria     = oliguria_xlsx    ,
    creatinine   = creatinine_xlsx  ,
    demographics = demographics_xlsx,
    time_series  = creat_furo_xlsx
  )
  return(xlsx_data)
}

xlsx_data <- suppressMessages(load_excel_files())
```

```{r convert Excel dates fun}
excel_date_to_character <- function(vector) {
  suppressWarnings(
  ifelse(
    grepl("/", vector), 
    vector, 
    as.character(as.Date(as.numeric(vector), origin = "1899-12-30"), format = "%d/%m/%y"))
  )
}

convert_excel <- function(xlsx_data) {
  xlsx_data$oliguria$screen_log   %<>% arrange(`UR number`, Dates_screened) %>% 
    mutate(Dates_screened = excel_date_to_character(Dates_screened))
  xlsx_data$creatinine$screen_log %<>% arrange(`UR number`, Dates_screened) %>% 
    mutate(Dates_screened = excel_date_to_character(Dates_screened))
  return(xlsx_data)
}

```

```{r convert Excel dates, echo=TRUE}
xlsx_data <- convert_excel(xlsx_data)
```

## Screening logs

### Data Collection Errors

Checks were made on the data collection screening log. Errors were identified and they were corrected as `Excl_criteria_ok = "N"` and `"Already_AKI" = "Y"` to be consistent with previous corrections made for @citation{Toh2019}. Additional changes were made in order to prevent errors merging databases.

The discarded patient study numbers are listed below. These are consistent with the rejected numbers for @citatin{Toh2019}

```{r data collection errors fun}
data_collection_errors <- function(xlsx_data) {
  errors_logi = 
    (xlsx_data$creatinine$screen_log$`UR number`      != xlsx_data$oliguria$screen_log$`UR number`     ) |
    (xlsx_data$creatinine$screen_log$Dates_screened   != xlsx_data$oliguria$screen_log$Dates_screened  ) |
    (xlsx_data$creatinine$screen_log$Excl_criteria_ok != xlsx_data$oliguria$screen_log$Excl_criteria_ok)
  creatinine_errors = xlsx_data$creatinine$screen_log[errors_logi, ]
  oliguria_errors   = xlsx_data$oliguria  $screen_log[errors_logi, ]
  
  xlsx_data$excluded_UR_numbers  = creatinine_errors$`UR number`
  xlsx_data$excluded_Pt_Study_no = discard(c(oliguria_errors$Pt_Study_no, creatinine_errors$Pt_Study_no), is.na)
  
  cat("Creatinine xlsx sheet inconsistencies\n")
  print(creatinine_errors[, c(13, 2:4)])
  cat("\nOliguria xlsx sheet inconsistencies\n"  )
  print(oliguria_errors  [, c(13, 2:4)])
  
  cat(paste("\n",
    # "Discarded UR Numbers:       ", paste(xlsx_data$excluded_UR_numbers , collapse = ", "), "\n",
    "Discarded Pt Study Numbers: ", paste(xlsx_data$excluded_Pt_Study_no, collapse = ", "), "\n"
  ))
  
  # Discard data from xlsx_data
  xlsx_data$creatinine$screen_log[errors_logi, "Dates_screened"] = 
    xlsx_data$oliguria$screen_log[errors_logi, "Dates_screened"]
  
  xlsx_data$creatinine$screen_log[errors_logi, "Excl_criteria_ok"  ] = "N"
  xlsx_data$creatinine$screen_log[errors_logi, "Incl_criteria_ok"  ] = NA
  xlsx_data$creatinine$screen_log[errors_logi, "Already_AKI"       ] = "Y"
  xlsx_data$creatinine$screen_log[errors_logi, "Epis_cr_change"    ] = NA
  xlsx_data$creatinine$screen_log[errors_logi, "Total_no_cr_epis"  ] = NA
  
  xlsx_data$oliguria  $screen_log[errors_logi, "Excl_criteria_ok"  ] = "N"
  xlsx_data$oliguria  $screen_log[errors_logi, "Incl_criteria_ok"  ] = NA
  xlsx_data$oliguria  $screen_log[errors_logi, "Already_AKI"       ] = "Y"
  xlsx_data$oliguria  $screen_log[errors_logi, "Epis_olig"         ] = NA
  xlsx_data$oliguria  $screen_log[errors_logi, "Total_no_olig_epis"] = NA
  
  return(xlsx_data)
}

```

```{r data collection errors, echo=TRUE}
xlsx_data = data_collection_errors(xlsx_data)
```


### Merging of Screening Logs

The screening logs were merged by common columns. Columns that had the same heading but different meanings in the 'Creatinine Change in Oliguria' and  'Small changes in creatinine' where given suffixes of `_olig` and `_crch` respsectively. These columns were:

* `Incl_criteria_ok`: Different between oliguria and creatinine change
* `Pt_Study_no`: Different, `L` or `LT`
* `Comment`: Specific to each data collection

```{r merge screening logs fun}
merge_xlsx_screening <- function(xlsx_data) {
  merge_columns = setdiff(
    intersect(colnames(xlsx_data$creatinine$screen_log), 
              colnames(xlsx_data$oliguria$screen_log)),
    c("Incl_criteria_ok", "Pt_Study_no", "Comment")
  )
  analysis_data = full_join(
    xlsx_data$creatinine$screen_log,
    xlsx_data$oliguria  $screen_log,
    by     = merge_columns,
    suffix = c("_crch", "_olig")
    )
  
  if (anyNA(analysis_data$`UR number`)) {
    stop("NA in UR number of merged Excel sheets")
  }
  
  creatinine_n_obs = nrow(xlsx_data$creatinine$screen_log)
  oliguria_n_obs   = nrow(xlsx_data$oliguria  $screen_log)
  analysis_n_obs   = nrow(analysis_data)
  if (length(unique(c(creatinine_n_obs, oliguria_n_obs, analysis_n_obs))) != 1) {
    stop(paste0(
      "Inconsistent number of n_obs after UR numbers discarded. ",
      "Creatinine: ", creatinine_n_obs, ", ",
      "Oliguria: "  , oliguria_n_obs  , ", ",
      "Merged: "    , analysis_n_obs  , ", "))
  }
  
  logi_colnames <- colnames(analysis_data)[
    !grepl("UR number|Dates_screened|Pt_Study_no|Total_no_|Comment", colnames(analysis_data))]
  analysis_data <- analysis_data %>% 
    mutate_at(logi_colnames, function(x) if_else(x == "N", FALSE, TRUE))

  return(analysis_data)
}

```

```{r merge screening logs, echo=TRUE}
analysis_data <- merge_xlsx_screening(xlsx_data)
glimpse(analysis_data)
```

## Data Sets

Both 'Creatinine Change in Oliguria' and  'Small changes in creatinine' had data sets that included:

* `Patient Demographics`
* `AKI & Outcomes`
* `Screening log`

Each of these was combined, then combined with the other data collection spreadsheet. The number of observations was checked throughout to ensure there were no patients duplicated/removed.

```{r merge Excel sheets together fun, echo=FALSE}
dttm_cols <- function(text, colnames) {
  cols <- data.frame(
    i = grep(paste0("^", text, "|", text, "$"), colnames, ignore.case = TRUE),
    j = grep(paste0("^", text, "|", text, "$"), colnames, ignore.case = TRUE, value = TRUE),
    stringsAsFactors = FALSE
  ) %>% 
    mutate(k = gsub(text, "DateTime", j, ignore.case = TRUE))
  colnames(cols) <- c(paste0(text, "_i"), paste0(text), "match")
  
  return(cols)
}

merge_data_set_demo_outcomes <- function(data,excluded_Pt_Study_no,
                                         data_name = deparse(substitute(data))) {
  combined_data <-data$data_set %>% 
    fill(Pt_Study_no) %>% 
    full_join(., data$demographic, by = "Pt_Study_no") %>% 
    full_join(., data$outcomes   , by = "Pt_Study_no")
  if (nrow(combined_data) != nrow(data$data_set)) {
    stop(paste0(
      "Inconsistent number of rows after merging data_set with demographics and outcomes",
      "Data: "         , data_name          , ", ",
      "Data set rows: ", nrow(data$data_set), ", ",
      "Merged rows: "  , nrow(combined_data), ", "
    ))
  }
  
  dttm_col = inner_join(
    dttm_cols("date", colnames(combined_data)),
    dttm_cols("time", colnames(combined_data)), by = "match") %>% 
    select(date, time, match)
  # Instead, consider using mutate_at to convert date and time columns and paste
  # then into the date columns. Then use rename at to conver to a datetime name
  # and then remove the time columns.
  
  combined_data <- combined_data %>% 
    select(-last_col()) %>% 
    filter(!(Pt_Study_no %in% excluded_Pt_Study_no)) %>% 
    pivot_longer(
      cols = c(dttm_col$date, dttm_col$time),
      names_to = "dttm_name",
      values_to = "dttm"
    ) %>% 
    mutate(
      type = if_else(grepl("date", dttm_name, ignore.case = TRUE), "date", "time"),
      dttm_name = gsub("date|time", "DateTime", dttm_name, ignore.case = TRUE)
    ) %>% 
    pivot_wider(
      names_from = "type",
      values_from = "dttm"
    ) %>% 
    mutate(
      datetime = ifelse(
        (is.na(date) | is.na(time)),
        NA,
        paste(
          format(date, format = "%Y-%m-%d"),
          format(time, format = "%H:%M:%S")
      )),
      date = NULL,
      time = NULL
    ) %>% 
    pivot_wider(
      names_from = "dttm_name",
      values_from = "datetime"
    )
  
  return(combined_data)
}
```

```{r merge Excel files together fun,echo=FALSE}
merge_xlsx_creatinine_oliguria <- function(analysis_data, xlsx_data) {
  creatinine = merge_data_set_demo_outcomes(xlsx_data$creatinine, xlsx_data$excluded_Pt_Study_no)
  oliguria   = merge_data_set_demo_outcomes(xlsx_data$oliguria  , xlsx_data$excluded_Pt_Study_no)
  
  colnames(creatinine)[1] = "Pt_Study_no_crch"
  colnames(oliguria  )[1] = "Pt_Study_no_olig"
  
  both <- suppressMessages(full_join(creatinine, oliguria))
  
  Total_no_cr_epis = sum(analysis_data$Total_no_cr_epis, na.rm = TRUE)
  if (length(unique(c(
    nrow(creatinine), length(which(!is.na(both$Pt_Study_no_crch))), Total_no_cr_epis))) != 1) 
    {
    stop(paste0(
      "Number of creatinine episodes is not consistent", 
      "Merged xlsx creatinine data: "   , nrow(creatinine), ", ",
      "Merged creatinine and oliguria: ", length(which(!is.na(both$Pt_Study_no_crch))), ", ",
      "Merged screening log number: "   , Total_no_cr_epis))
  }
  Total_no_olig_epis = sum(analysis_data$Total_no_olig_epis, na.rm = TRUE)
  if (length(unique(c(
    nrow(oliguria), length(which(!is.na(both$Pt_Study_no_olig))), Total_no_olig_epis))) != 1) 
    {
    stop(paste0(
      "Number of oliguria episodes is not consistent", 
      "Merged xlsx oliguria data: "     , nrow(oliguria), ", ",
      "Merged creatinine and oliguria: ", length(which(!is.na(both$Pt_Study_no_olig))), ", ",
      "Merged screening log number: "   , Total_no_olig_epis))
  }

  analysis_data <- suppressMessages(full_join(analysis_data, both))
  
  return(analysis_data)
}
```

```{r merge data sets}
analysis_data = merge_xlsx_creatinine_oliguria(analysis_data, xlsx_data)
glimpse(analysis_data)
```