# Load Data

```{r 01_load_data, include=FALSE, cache=FALSE}
knitr::read_chunk("R/02_load_data.R")
```

## Excel Data

Here we load the data from the previous study [toh2019]

```{r, excel_date_to_character_function, echo=FALSE}
```

```{r, last_column_as_comment_function, echo=FALSE}
```

```{r, load_excel}
```

## Anonymise Data

Save old `UR number` here. Replace `UR number` with hash.

## Identify Potential Data Collection Errors

```{r, data_collection_errors}
```


# Screening Log

```{r 02_screening_log, include=FALSE, cache=FALSE}
knitr::read_chunk("R/03_screening_log.R")
```

## Merge Screening Log

```{r, join_demo_screen_log_sheets_function, echo=FALSE}
```

```{r, screen_log_all}
```

## APACHE Database

Merge in the APACHE database to replace missing values (`NA`) and empty values (`-Inf`).

```{r, screen_log_apache}
```

## Admission Overview

```{r, screen_log_overview}
```


# Obs Data Set
```{r 03_data_set, include=FALSE, cache=FALSE}
knitr::read_chunk("R/04_data_set.R")
```

## Merge Data Set

```{r, find_cols_function, echo=FALSE}
```

```{r, merge_data_sets_outcomes}
```

```{r, merge_data_sets}
```

## Episode Overview

```{r, epis_overview}
```


# Time Series Data

## Creatinine

## Frusemide
